---
title: "lab_6"
author: "Daija Odom"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

 # Learned about flavors of rank-based tests in Lecture 11

We'll make our own samples, using a pseudorandom generator. 
# Looked at `?set.seed` in console
# set.seed is when I ask R to create a set of integer values behind the scenes, sets the starting point from which the vector is pulled (mostly likely won't use in this class)

```{r}
set.seed(1414) #1414 is just the number of the room we are in
gp_1 <- sample.int(20, size = 15, replace = TRUE) # Sample contains integer values of up to 20 (highest value it will go up to), with 15 samples in it

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

```{r}
# For exploratory purposes
hist(gp_1) # Does not convince you of normal distribution

hist(gp_2) # Does not convince you that you should assume these are normally distributed
```

Try a t-test:
```{r}
t.test(gp_1, gp_2)
```

What is the meaning of the p-value?

If these samples were drawn from populations with the same mean, the probability of taking two random samples with means *at least as different* as the sample means we found by random chance (taking into account spread, n) is 19.8%. 


Retain (fail to reject) the null hypothesis. >> There is no significant difference in means between group 1 and group 2. 
# You do not have sufficient evidence to reject the null hypothesis

Warning: people get weirdly upset if you say "accept" the null.

Now let's compare this outcome to a rank-based test.

## Mann Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2) # Stores the test in your environment

mwu # you can type ?wilcox.test in the console and scroll down to `values` to learn what is in this test or you can click the stored value in the environment tab. Values shows you further descriptions.
```

If these samples were drawn from populations with the same ranks (medians), the probability of finding two samples with ranks *at least as different* as those in our samples is 0.28. 


Is that so unlikely to have happened that i have evidence to reject that null hypothesis?

There is no significant difference in ranks (often you'll see medians) between group 1 and group 2 (statistical summary).

Median scores for group 1 (M = 14) and group 2 (M = 12) did not differ significantly (Mann Whitney U test: U(df) = 86, p = 0.28).

# *You will get points off*  When you decide the appropriate type of statistical test, everything you report needs to line up with that throughout the analysis.

## Linear regression

Simple linear regression (single dependent variable, a single independent variable)

```{r, include = FALSE}
# Make an exploratory plot of penguin body mass (y-axis) versus flipper length (x-axis)
# Set code chunk options `include` nothing from that code chunk will show up in knitted document

ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() +
  geom_smooth(method = "lm") # If you don't know how to explain/interpret this line and model,it should not be on there. 

# No outliers appears on graph that would sway this model 
```

Find a linear regression model using ordinary least squares describing the relationship between flipper length and body mass for these penguins.

3 pieces:

- What type of model?
- What is the relationship to model (DV ~ IV(s))
- Where is the data that's used to create this model?

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins) 
# lm is used to fit linear models. Change as a function of flipper length. tell it where to pull the data from 
# y = mx + b
# y = B1x + B0 + E (body mass is `y`,flipper length is the predictor variable `B1x`)
# call penguin_lm in the console
```

Bodymass = 49.7(Flipper length) 5780.8 (has to be in g)
# Bodymass is in g and flipper length is in mm so mathematically 49.7 has to be in g/mm  

#Type in the console to see elements of the data
# penguin_lm$coefficients
      (Intercept) flipper_length_mm 
      -5780.83136          49.68557 
      
# penguin_lm$coefficients[2]
flipper_length_mm 
         49.68557

### broom package returns model outputs as tidy data fram
         
```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm) # broom is a part of tidyverse but is not a part of tidyverse core so you need to attach it

penguin_lm_tidy

broom::glance(penguin_lm) # Gives you model wide data frame. Talk more about this on Wednesday
```

How can I actually include my model equation in a report?

```{r}
extract_eq(model = penguin_lm)
```

```{r}
plot(penguin_lm)

# 2nd Q-Q plot explores normality of the residuals. Are the residuals normally distributed? This plot specifically answers yes
# 1st and 3rd graph are about spread of residuals
# 4th plot is a weight of points; it's a way of considering outliers 
```

