---
title: "lab_6"
author: "Daija Odom"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

 # Learned about flavors of rank-based tests in Lecture 11

We'll make our own samples, using a pseudorandom generator. 
# Looked at `?set.seed` in console
# set.seed is when I ask R to create a set of integer values behind the scenes, sets the starting point from which the vector is pulled (mostly likely won't use in this class)

```{r}
set.seed(1414) #1414 is just the number of the room we are in
gp_1 <- sample.int(20, size = 15, replace = TRUE) # Sample contains integer values of up to 20 (highest value it will go up to), with 15 samples in it

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

```{r}
# For exploratory purposes
hist(gp_1) # Does not convince you of normal distribution

hist(gp_2) # Does not convince you that you should assume these are normally distributed
```

Try a t-test:
```{r}
t.test(gp_1, gp_2)
```

What is the meaning of the p-value?

If these samples were drawn from populations with the same mean, the probability of taking two random samples with means *at least as different* as the sample means we found by random chance (taking into account spread, n) is 19.8%. 


Retain (fail to reject) the null hypothesis. >> There is no significant difference in means between group 1 and group 2. 
# You do not have sufficient evidence to reject the null hypothesis

Warning: people get weirdly upset if you say "accept" the null.

Now let's compare this outcome to a rank-based test.

## Mann Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2) # When you run it you receive a warning not an error message

mwu
```

If these samples were drawn from populations with the same ranks (medians), the probability of finding two samples with ranks *at least as different* as those in our samples is 0.28. 


Is that so unlikely to have happened that i have evidence to reject that null hypothesis?

There is no significant difference in ranks (often you'll see medians) between group 1 and group 2 (statistical summary).

Median scores for group 1 (M = 14) and group 2 (M = 12) did not differ significantly (Mann Whitney U test: U(df) = 86, p = 0.28).

# *You will get points off*  When you decide the appropriate type of statistical test, everything you report needs to line up with that throughout the analysis.

